---
title: "IDA Gossip Experiment Results"
author: "Kadir Korkmaz"
date: "7/1/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Experimental Setup

4096 process deployed on 32 machines---128 process per machine---from Gros cluster(G5K).
The bandwidth of each process capped at 20Mbps(Upload Bandwidth). 
One way latency of 15ms added to each communication link(RTT is 30ms).

In this set of experiments, a large message---2MB--- chunked in to 128 chunks and disseminated over different number of sources usin IDA gossip.
1 source means that the full message is disseminated by the single source.
2 source means that the message disseminated over 2 source each disseminate 64 chunks.

Each experiment run for 120 rounds to collect enough data.

A rounds ends for a node when it collects all of the 128 chunks disseminated in that round. At the end of a round, a node calculates a sleep time and sleeps. ***The sleep time is implemented to see the best possible performance of the IDA gossip.***

Currently, IDA gossip implementation does not add redundancy chunks because the number of redundancy chunks are calculated according to the percentage of faulty nodes in the system.

Currently, we have measured 3 metrics:

* First Chunk Delivery Time (ms)
* Message Delivery Time (ms)
* Queue Length

First Chunk Delivery Time is the measure of how early a node can contribute to the dissemination, and the smaller value is desirable.
Message Delivery Time is the time needed to collect all 128 chunks disseminated for that round. Each message contains a time field, and this field is used to calculate elapsed time by a node. Queue length is the average number of messages on peers waiting to be forwarded. Queue length could be the precursor of contention: chunks are competing for the same resources and queue size could be helpful to understand the extend of this contention.

## Table of Contents
Page 2 contains the plots, and page 3 contains data used in plots.

\newpage

```{r first_chunk_delivery, echo=FALSE}
library(ggplot2)

folder_path <- "/home/kadir/Desktop/ida-experiments-no-break/"

df_chunks <- read.csv(paste(folder_path, "first_chunk_delivery_df.tsv", sep = ""), sep = "\t", header = TRUE)
p1 <- ggplot(df_chunks, aes(x=as.factor(SourceCount))) +
      geom_boxplot(aes(
        ymin=Min,
        lower= FirstQuartile,
        middle=Median,
        upper=ThirdQuartile,
        ymax=Max
      ), stat="identity") + 
      ylab("First Chunk Delivery Time(ms)") + 
      xlab("Source Count") + 
      expand_limits(y = 0)

```


```{r message_delivery, echo=FALSE}

df_message_delivery <- read.csv(paste(folder_path, "message_received_df.tsv", sep = ""), sep = "\t", header = TRUE)
p2 <- ggplot(df_message_delivery, aes(x=as.factor(SourceCount), y=Mean)) +
      geom_errorbar(aes(ymin=LowerBound, ymax=UpperBound), width=.3)+
      geom_point() + 
      ylab("Mean Time to Deliver Message(ms)") +  
      xlab("Source Count") +
      expand_limits(y = 0)
      

```

```{r queue_length, echo=FALSE, fig.height=3}

df_queue_length <- read.csv(paste(folder_path, "queue_length_df.tsv", sep = ""), sep = "\t", header = TRUE)
p3 <- ggplot(df_queue_length, aes(x=as.factor(SourceCount), y=Mean)) +
      geom_errorbar(aes(ymin=LowerBound, ymax=UpperBound), width=.3)+
      geom_point() + 
      ylab("Mean Queue Length") +  
      xlab("Source Count") +
      expand_limits(y = 0) 

```



```{r allign_plots, echo=FALSE, fig.height=8, fig.width=8}

library(gridExtra)

#p1 <- p1 + theme(axis.title.x = element_blank()) 
#p2 <- p2 + theme(axis.title.x = element_blank()) 
#p3 <- p3 + theme(axis.title.x = element_blank()) 

plots <- list( p1, p2, p3 )
grobs <- list()
widths <- list()

for (i in 1:length(plots)){
    grobs[[i]] <- ggplotGrob(plots[[i]])
    widths[[i]] <- grobs[[i]]$widths[2:5]
}

maxwidth <- do.call(grid::unit.pmax, widths)

for (i in 1:length(grobs)){
     grobs[[i]]$widths[2:5] <- as.list(maxwidth)
}

do.call( "grid.arrange", c(grobs, ncol = 1) )

```


\newpage
```{r, echo=FALSE}
suppressPackageStartupMessages(library(dplyr))
library(knitr)




df_chunks <- df_chunks %>% select( SourceCount, Min, FirstQuartile, Median, ThirdQuartile, Max) %>% arrange( SourceCount )
kable(df_chunks, caption = "First Chunk Delivery Time(ms)")

df_message_delivery <- df_message_delivery  %>% select( SourceCount, LowerBound, Mean, UpperBound) %>% arrange( SourceCount )
kable(df_message_delivery, caption = "Mean Message Delivery Time(ms)")


df_queue_length <- df_queue_length  %>% select( SourceCount, LowerBound, Mean, UpperBound) %>% arrange( SourceCount )
kable(df_queue_length, caption = "Queue Length")

```



