---
title: "IDA Gossip Experiment Results"
author: "Kadir Korkmaz"
date: "7/22/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

\newpage

```{r first_chunk_delivery, echo=FALSE}
library(ggplot2)


mb_to_bytes<-1048576

folder_path <- "/home/kadir/Desktop/ida-gossip-experiments/faults_injected_fanout8/"

### MessageSize
#target_variable <- as.name("MessageSize")
#x_label="Message Size(MB)"

### FaultyNodePercent
target_variable <- as.name("FaultyNodePercent")
x_label="Faulty Node Percent"


df_chunks <- read.csv(paste(folder_path, "first_chunk_delivery_df.tsv", sep = ""), sep = "\t", header = TRUE)
df_chunks$MessageSize = df_chunks$MessageSize / mb_to_bytes



```


```{r message_delivery, echo=FALSE}

df_message_delivery <- read.csv(paste(folder_path, "message_received_df.tsv", sep = ""), sep = "\t", header = TRUE)
df_message_delivery$MessageSize = df_message_delivery$MessageSize / mb_to_bytes


```



```{r delivered_messages, echo=FALSE}

df_delivery_percent <- data.frame(df_message_delivery) 

df_delivery_percent$DeliveryPercent <- (df_message_delivery$RowCount/df_message_delivery$ExperimentCount) * 100 / df_message_delivery$NodeCount

```




\newpage
```{r, echo=FALSE}
suppressPackageStartupMessages(library(dplyr))
library(knitr)

names(df_chunks)[names(df_chunks) == 'MessageChunkCount'] <- "ChunkCount"
names(df_message_delivery)[names(df_message_delivery) == 'MessageChunkCount'] <- "ChunkCount"
names(df_delivery_percent)[names(df_delivery_percent) == 'MessageChunkCount'] <- "ChunkCount"


df_chunks <- df_chunks %>% select( !!target_variable, ChunkCount, Min, FirstQuartile, Median, ThirdQuartile, Max, Mean, RowCount) %>% arrange( !!target_variable, ChunkCount )

# converts ms to S
df_chunks$FirstQuartile <- df_chunks$FirstQuartile / 1000
df_chunks$Median <- df_chunks$Median / 1000
df_chunks$ThirdQuartile <- df_chunks$ThirdQuartile / 1000

```

\newpage
```{r, echo=FALSE}

df_message_delivery <- df_message_delivery  %>% select( !!target_variable, ChunkCount,  Min, FirstQuartile, Median, ThirdQuartile, Max, Mean, RowCount) %>% arrange( !!target_variable, ChunkCount )

# converts ms to S
df_message_delivery$FirstQuartile <- df_message_delivery$FirstQuartile / 1000
df_message_delivery$Median <- df_message_delivery$Median / 1000
df_message_delivery$ThirdQuartile <- df_message_delivery$ThirdQuartile / 1000
```


\newpage

```{r, echo=FALSE}

df_delivery_percent$DeliveryPercent

df_delivery_percent <- df_delivery_percent  %>% select( !!target_variable, ChunkCount,  Min, FirstQuartile, Median, ThirdQuartile, Max, Mean, DeliveryPercent) %>% arrange( !!target_variable, ChunkCount )

```

\newpage
#```{r, echo=FALSE, fig.width=3.5, fig.height=4.5}
```{r, echo=FALSE, fig.width=5, fig.height=6}

#https://waterdata.usgs.gov/blog/beyond-basic-plotting/

df_chunks <- df_chunks %>% select( !!target_variable, ChunkCount, Median,FirstQuartile,ThirdQuartile) %>% rename( ChunkDelivery = Median)
df_message_delivery <- df_message_delivery  %>% select( !!target_variable, ChunkCount, Median,FirstQuartile,ThirdQuartile) %>% rename( MessageDelivery = Median)
df_delivery_percent <- df_delivery_percent  %>% select( !!target_variable, ChunkCount, DeliveryPercent,FirstQuartile,ThirdQuartile)


library(reshape)

df_chunks.melted <- melt(df_chunks, id=c("FaultyNodePercent","ChunkCount", "FirstQuartile", "ThirdQuartile"))
df_message_delivery.melted <- melt(df_message_delivery, id=c("FaultyNodePercent","ChunkCount", "FirstQuartile", "ThirdQuartile"))
df_delivery_percent.melted <- melt(df_delivery_percent, id=c("FaultyNodePercent","ChunkCount", "FirstQuartile", "ThirdQuartile"))

df_delivery_percent.melted$FirstQuartile <- NA
df_delivery_percent.melted$ThirdQuartile <- NA

merged_df <- rbind( df_chunks.melted, df_message_delivery.melted )
merged_df <- rbind( merged_df, df_delivery_percent.melted )

melted_df <- merged_df

p <- ggplot(melted_df, aes(x= as.factor(!!target_variable), y=value,  group=ChunkCount, color=as.factor(ChunkCount), linetype=as.factor(ChunkCount), shape=as.factor(ChunkCount) )) +
      geom_line()+
      geom_point()+
      geom_errorbar( aes(ymin=FirstQuartile, ymax=ThirdQuartile), width=0.1, alpha=1, size=0.2)+
      expand_limits(y = 0) +
      labs(color='Chunk Count', shape='Chunk Count', linetype='Chunk Count') +
      theme_bw()+
      theme(legend.position="top") +
      ylab(NULL) +
      xlab("Faulty Node Percent") +
      theme(strip.background = element_blank(), # remove the background
          strip.placement = "outside", legend.margin=margin(0,-0,-6,0))

#, switch = "y"
p <- p + facet_grid(variable ~ ., scales = "free_y", switch = "y", labeller = as_labeller(
      c(ChunkDelivery = "First Chunk Latency (S)", MessageDelivery = "Latency (S)", DeliveryPercent = "Coverage (%)"))
  ) + theme(plot.margin = margin(0,0.5,0,0, "cm")) #+ scale_y_continuous(labels = function(x) format(x, scientific = TRUE))

p <- p + theme(text = element_text(family="Times", face="plain", size=12), strip.text.y=element_text(family="Times", face="plain", size=12))

p


ggsave("faults.pdf", p)


```


